---
title       : Course Project- Shiny Application and Reproducible Pitch
subtitle    : 
author      : Yu-Fen Wang
date        : 2017/11/05
job         : 
framework   : html5slides        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : [mathjax,boostrap]            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## Pitch

This is the pitch presentation of the app I created as the Data Product course project 
In this presentation, I will enclose the code I made the app and the link to the app


--- 

## The function of this app 

The data covers the Daily Closing Prices of Major European Stock Indices from 1991-1998
The indices are: Germany DAX (Ibis), Switzerland SMI, France CAC, and UK FTSE.

I created an app in which you can choose one of these 4 indices and it will automatively plot its closing price from 1991-1998 for you. 


---

## Code for the server.R
```{r echo=TRUE}
library(shiny)
library(datasets)
data("EuStockMarkets")

# Define server logic required to draw a histogram
shinyServer(function(input, output) {
   
  output$Plot <- renderPlot({
     # generate dataset from input
    if (input$index=="DAX"){
        plot(EuStockMarkets[,1],ylab="DAX closing price",xlab="Year")
    } else if (input$index=="SMI"){
        plot(EuStockMarkets[,2],ylab="SMI closing price",xlab="Year")
    }else if (input$index=="CAC"){
        plot(EuStockMarkets[,3],ylab="CAC closing price",xlab="Year")
    }else{
        plot(EuStockMarkets[,4],ylab="FTSE closing price",xlab="Year")
    }

    
  })
  
})

```


--- 

## code for the ui.R

```{r}
library(shiny)
library(datasets)
data("EuStockMarkets")

# Define UI for application that draws a histogram
shinyUI<-fluidPage(
  
  # Application title
  titlePanel("Closing Prices of Major European Stock from 1991 to 1998"),
  
  # Sidebar with a slider input for number of bins 
  sidebarLayout(
    sidebarPanel(
       ## select index type
        radioButtons("index", "Please Select Index:",
                     c("DAX" = "DAX",
                       "SMI" = "SMI",
                       "CAC" = "CAC",
                       "FTSE" = "FTSE"))
    ),
    
    # Show a plot of the generated distribution
    mainPanel(
       plotOutput("Plot")
    )
  )
)

```

---
## you may find the link as followed:
https://andrea-yufen-wang.shinyapps.io/Data_product_project/

Thank you!

